---
title: "CMS Lite Traffic Monitoring"
logo: "www/bcstats_logo_rev.png"
format: 
  dashboard:
    theme:
      - litera
      - theme.scss
    orientation: rows
    embed-resources: true
    nav-buttons:
      - icon: github
        href: https://github.com/bcgov/bcstats-webtraffic-monitoring
---

<!-- 
HOW TO RUN THIS DASHBOARD FOR CODE REVIEW:
Option 1: In Positron or RStudio, open this file and click the "Render" button at the top.
Option 2: Run the following in the R Console: `quarto::quarto_render("Report/cmslite_dashboard.qmd")`
Option 3: Run the following in the Terminal: `quarto preview Report/cmslite_dashboard.qmd`

Data is produced by R/02c-analyze-cmslite-data.R, which writes the cmslite_*.csv
tables to OUTPUT_TABLES.
-->

```{r setup, include=FALSE}
library(readr)
library(dplyr)
library(knitr)
library(ggplot2)
library(forcats)
library(plotly)
library(lubridate)
library(safepaths)
library(glue)
library(DT)
library(scales)

`%||%` <- function(a, b) if (is.null(a)) b else a

# Resolve OUTPUT_TABLES the same way 00-setup.R does.
LAN_FOLDER <- use_network_path()
PROJECT_ROOT <- glue("{LAN_FOLDER}/0. Misc/Data Science Tooling/web-hosting-and-dashboards/shinyapps_webtraffic_monitoring")
OUTPUT_TABLES <- glue("{PROJECT_ROOT}/outputs/tables")

# Read a cmslite CSV if it exists; otherwise return NULL so govstats-only
# sections degrade gracefully instead of erroring.
read_cmslite <- function(name) {
  path <- file.path(OUTPUT_TABLES, name)
  if (file.exists(path)) {
    read_csv(path, show_col_types = FALSE)
  } else {
    NULL
  }
}

daily          <- read_cmslite("cmslite_daily.csv")
top_pages      <- read_cmslite("cmslite_top_pages.csv")
clicks_daily   <- read_cmslite("cmslite_clicks_daily.csv")
top_targets    <- read_cmslite("cmslite_top_targets.csv")
top_referrers  <- read_cmslite("cmslite_top_referrers.csv")
by_os          <- read_cmslite("cmslite_by_os.csv")
by_geo         <- read_cmslite("cmslite_by_geo.csv")
asset_daily    <- read_cmslite("cmslite_asset_downloads_daily.csv")
top_assets     <- read_cmslite("cmslite_top_assets.csv")
search_terms   <- read_cmslite("cmslite_search_terms.csv")
google_queries <- read_cmslite("cmslite_google_queries.csv")

# Sites present in the data (data-driven).
sites <- sort(unique(daily$site))

# Friendly labels; coalesce() keeps unknown sites working.
site_label_map <- c(
  outcomes   = "Outcomes (outcomes.bcstats.gov.bc.ca)",
  antiracism = "Anti-Racism (antiracism.gov.bc.ca)",
  govstats   = "BC Stats / Statistics (gov.bc.ca)"
)
site_label <- function(s) coalesce(unname(site_label_map[s]), s)

site_short_map <- c(
  outcomes   = "Outcomes",
  antiracism = "Anti-Racism",
  govstats   = "BC Stats"
)
site_short <- function(s) coalesce(unname(site_short_map[s]), s)

# BC-blue family palette, keyed by site, with grey fallback.
site_palette_pool <- c("#003366", "#1F6B75", "#9E4C1A", "#6C3D8A", "#2F6B3F", "#B07D12")
site_colors <- setNames(
  site_palette_pool[seq_along(sites)],
  sites
)
site_colors[is.na(site_colors)] <- "#888888"

# Date range covered by the data (used in titles/subtitles).
date_min <- min(daily$date, na.rm = TRUE)
date_max <- max(daily$date, na.rm = TRUE)
date_range_str <- if (format(date_min, "%Y-%m") == format(date_max, "%Y-%m")) {
  format(date_min, "%B %Y")
} else {
  paste0(format(date_min, "%b %d, %Y"), " \u2013 ", format(date_max, "%b %d, %Y"))
}

# Month-to-date totals across all sites (for value boxes).
total_page_views <- sum(daily$page_views, na.rm = TRUE)
total_sessions   <- sum(daily$sessions, na.rm = TRUE)
total_clicks     <- if (!is.null(clicks_daily)) sum(clicks_daily$clicks, na.rm = TRUE) else 0L

# Engagement: page views per session (avoids the daily-unique over-count of users).
pv_per_session <- if (total_sessions > 0) total_page_views / total_sessions else NA_real_

# Shared Plotly branding helpers (match shinyapps_dashboard.qmd).
bc_font <- list(family = "BC Sans, Segoe UI, Arial, sans-serif")

plotly_config <- list(
  displaylogo = FALSE,
  modeBarButtonsToRemove = list(
    "zoom2d", "pan2d", "select2d", "lasso2d",
    "zoomIn2d", "zoomOut2d", "autoScale2d",
    "hoverClosestCartesian", "hoverCompareCartesian"
  ),
  responsive = TRUE
)

# Shorten a long display URL for axis labels; full value kept for hover.
# Intentionally used only by the Top Downloaded Assets chart now; the page,
# referrer, and location charts display full labels.
shorten_url <- function(x, max_chars = 55) {
  x <- ifelse(is.na(x) | x == "" | x == "(not set)", "(unknown)", x)
  # Drop scheme + host so the path stands out.
  stripped <- sub("^https?://[^/]+", "", x)
  stripped <- ifelse(stripped == "" | stripped == "/", x, stripped)
  ifelse(
    nchar(stripped) > max_chars,
    paste0("\u2026", substr(stripped, nchar(stripped) - max_chars + 1, nchar(stripped))),
    stripped
  )
}

# Build a horizontal bar chart with a per-site dropdown (one trace per site).
# `data` must have columns: site, <label_col>, <value_col>, and optionally
# `full_label` (used for hover; falls back to <label_col>).
# When `pre_aggregate = TRUE`, values are summed by label within each site before
# ranking (e.g. region/country rows that repeat within a site).
# Ordering is enforced per site via yaxis categoryarray so the largest value is
# always at the top, including after switching sites via the dropdown.
site_dropdown_barh <- function(data, label_col, value_col, value_name,
                               title_prefix, top_n = 15, pre_aggregate = FALSE) {
  site_list <- sort(unique(data$site))

  has_full <- "full_label" %in% names(data)

  prep_site <- function(s) {
    d <- data |> filter(site == s)
    if (pre_aggregate) {
      group_cols <- if (has_full) c(label_col, "full_label") else label_col
      d <- d |>
        summarize(
          !!value_col := sum(.data[[value_col]], na.rm = TRUE),
          .by = all_of(group_cols)
        )
    }
    d |>
      arrange(desc(.data[[value_col]])) |>
      slice_head(n = top_n)
  }

  data_by_site <- lapply(site_list, prep_site)
  names(data_by_site) <- site_list

  default_site <- data |>
    summarize(v = sum(.data[[value_col]], na.rm = TRUE), .by = site) |>
    slice_max(v, n = 1) |>
    pull(site)

  p <- plot_ly()
  for (s in site_list) {
    d <- data_by_site[[s]]
    p <- add_bars(
      p,
      x = d[[value_col]],
      y = d[[label_col]],
      orientation = "h",
      visible = s == default_site,
      marker = list(color = unname(site_colors[s]),
                    line = list(color = "white", width = 0.5), opacity = 0.9),
      customdata = if (has_full) d$full_label else d[[label_col]],
      hovertemplate = paste0("<b>%{customdata}</b><br>", value_name, ": %{x:,}<extra></extra>"),
      showlegend = FALSE
    )
  }

  buttons <- lapply(seq_along(site_list), function(i) {
    s <- site_list[i]
    d <- data_by_site[[s]]
    vis <- rep(FALSE, length(site_list))
    vis[i] <- TRUE
    list(
      method = "update",
      args = list(
        list(visible = as.list(vis)),
        list(
          title = list(
            text = paste0("<b>", title_prefix, " \u2013 ", site_short(s), "</b>"),
            font = modifyList(bc_font, list(size = 15, color = "#003366"))
          ),
          yaxis = list(
            title = "", automargin = TRUE,
            tickfont = modifyList(bc_font, list(size = 10, color = "#2d2d2d")),
            categoryorder = "array", categoryarray = rev(d[[label_col]])
          )
        )
      ),
      label = site_short(s)
    )
  })

  default_d <- data_by_site[[default_site]]

  p |>
    layout(
      title = list(
        text = paste0("<b>", title_prefix, " \u2013 ", site_short(default_site), "</b>"),
        font = modifyList(bc_font, list(size = 15, color = "#003366"))
      ),
      xaxis = list(title = "", gridcolor = "#e8ecf0", zeroline = FALSE,
                   tickfont = modifyList(bc_font, list(size = 10, color = "#5c6b7a"))),
      yaxis = list(title = "", automargin = TRUE,
                   tickfont = modifyList(bc_font, list(size = 10, color = "#2d2d2d")),
                   categoryorder = "array", categoryarray = rev(default_d[[label_col]])),
      updatemenus = list(list(
        type = "dropdown", direction = "down",
        x = 0.0, xanchor = "left", y = 1.36, yanchor = "top",
        buttons = buttons,
        active = which(site_list == default_site) - 1L,
        showactive = TRUE, bgcolor = "#f5f8fb", bordercolor = "#c8d8e8",
        font = modifyList(bc_font, list(size = 11))
      )),
      plot_bgcolor = "#ffffff", paper_bgcolor = "#ffffff",
      margin = list(l = 10, r = 30, t = 115, b = 30), bargap = 0.3
    ) |>
    config(
      displaylogo = plotly_config$displaylogo,
      modeBarButtonsToRemove = plotly_config$modeBarButtonsToRemove,
      responsive = plotly_config$responsive
    )
}

```

# Summary {scrolling="true"}

## Row {height=210px}

::: {.valuebox color="primary" title="Total Page Views (All Sites, `r date_range_str`)"}
`r comma(total_page_views)`
:::

::: {.valuebox color="info" title="Total Sessions (All Sites, `r date_range_str`)"}
`r comma(total_sessions)`
:::

::: {.valuebox color="secondary" title="Page Views per Session (All Sites, `r date_range_str`)"}
`r formatC(pv_per_session, format = "f", digits = 2)`
:::

::: {.valuebox color="success" title="Total Clicks (All Sites, `r date_range_str`)"}
`r comma(total_clicks)`
:::

## Row {height=500px}

### Daily Page Views by Site

```{r}
trend_traces <- lapply(sites, function(s) {
  d <- daily |> filter(site == s) |> arrange(date)
  list(
    x = d$date, y = d$page_views, name = site_short(s),
    color = unname(site_colors[s])
  )
})

p_trend <- plot_ly()
for (tr in trend_traces) {
  p_trend <- add_trace(
    p_trend,
    x = tr$x, y = tr$y, type = "scatter", mode = "lines",
    name = tr$name, line = list(color = tr$color, width = 2),
    hovertemplate = paste0("<b>", tr$name, "</b><br>%{x|%b %d, %Y}<br>Page views: %{y:,}<extra></extra>")
  )
}

p_trend |>
  layout(
    title = list(
      text = paste0("<b>Daily Page Views by Site (", date_range_str, ")</b>"),
      font = modifyList(bc_font, list(size = 15, color = "#003366"))
    ),
    xaxis = list(title = "", gridcolor = "#e8ecf0", tickformat = "%b %d",
                 tickfont = modifyList(bc_font, list(size = 11, color = "#2d2d2d"))),
    yaxis = list(title = "", gridcolor = "#e8ecf0", automargin = TRUE,
                 tickfont = modifyList(bc_font, list(size = 11, color = "#5c6b7a"))),
    legend = list(orientation = "h", x = 0, y = -0.15,
                  font = modifyList(bc_font, list(size = 11)), title = list(text = "")),
    annotations = list(list(
      text = "Tip: Click a site in the legend to isolate its trend; click again to reset.",
      x = 1, y = -0.22, xref = "paper", yref = "paper",
      xanchor = "right", yanchor = "top", showarrow = FALSE,
      font = modifyList(bc_font, list(size = 10, color = "#8a9bac"))
    )),
    plot_bgcolor = "#ffffff", paper_bgcolor = "#ffffff",
    margin = list(l = 10, r = 20, t = 50, b = 80)
  ) |>
  layout(legend = list(itemclick = "toggleothers", itemdoubleclick = "toggle")) |>
  config(
    displaylogo = plotly_config$displaylogo,
    modeBarButtonsToRemove = plotly_config$modeBarButtonsToRemove,
    responsive = plotly_config$responsive
  )
```

## Row {height=520px}

### Top Pages by Page Views

```{r}
top_pages_plot <- top_pages |>
  mutate(full_label = page_url, label = page_url)

site_dropdown_barh(
  top_pages_plot,
  label_col = "label", value_col = "page_views",
  value_name = "Page views",
  title_prefix = "Top Pages by Page Views"
)
```

## Row {height=480px}

### Top Referrers {width=50%}

```{r}
top_ref_plot <- top_referrers |>
  filter(!is.na(referrer_url), referrer_url != "", referrer_url != "(unknown)") |>
  mutate(full_label = referrer_url, label = referrer_url)

site_dropdown_barh(
  top_ref_plot,
  label_col = "label", value_col = "page_views",
  value_name = "Page views",
  title_prefix = "Top Referrers", top_n = 12
)
```

### Operating System Share {width=50%}

```{r}
os_plot <- by_os |>
  mutate(
    pct = page_views / sum(page_views),
    .by = site
  ) |>
  mutate(site_lbl = site_short(site))

plot_ly(
  os_plot,
  x = ~site_lbl, y = ~page_views, color = ~os,
  type = "bar",
  hovertemplate = paste0("<b>%{x}</b><br>OS: %{fullData.name}<br>Page views: %{y:,}<extra></extra>")
) |>
  layout(
    barmode = "stack",
    title = list(
      text = "<b>Page Views by Operating System</b>",
      font = modifyList(bc_font, list(size = 15, color = "#003366"))
    ),
    xaxis = list(title = "", tickfont = modifyList(bc_font, list(size = 11, color = "#2d2d2d"))),
    yaxis = list(title = "", gridcolor = "#e8ecf0", automargin = TRUE,
                 tickfont = modifyList(bc_font, list(size = 10, color = "#5c6b7a"))),
    legend = list(font = modifyList(bc_font, list(size = 10)), title = list(text = "OS")),
    plot_bgcolor = "#ffffff", paper_bgcolor = "#ffffff",
    margin = list(l = 10, r = 20, t = 50, b = 30)
  ) |>
  config(
    displaylogo = plotly_config$displaylogo,
    modeBarButtonsToRemove = plotly_config$modeBarButtonsToRemove,
    responsive = plotly_config$responsive
  )
```

## Row {height=440px}

### Top Locations by Page Views

```{r}
geo_plot <- by_geo |>
  mutate(
    region = ifelse(is.na(region) | region == "", "(unknown)", region),
    country = ifelse(is.na(country) | country == "", "(unknown)", country),
    full_label = paste0(region, ", ", country),
    label = full_label
  )

site_dropdown_barh(
  geo_plot,
  label_col = "label", value_col = "page_views",
  value_name = "Page views",
  title_prefix = "Top Locations by Page Views",
  top_n = 12, pre_aggregate = TRUE
)
```

# BC Stats Extras {scrolling="true"}

```{r govstats-flags, include=FALSE}
has_assets <- !is.null(asset_daily) && nrow(asset_daily) > 0
has_search <- !is.null(search_terms) && nrow(search_terms) > 0
has_google <- !is.null(google_queries) && nrow(google_queries) > 0

total_downloads   <- if (has_assets) sum(asset_daily$downloads, na.rm = TRUE) else 0L
total_searches    <- if (has_search) sum(search_terms$searches, na.rm = TRUE) else 0L
total_g_clicks    <- if (has_google) sum(google_queries$clicks, na.rm = TRUE) else 0L
total_g_impress   <- if (has_google) sum(google_queries$impressions, na.rm = TRUE) else 0L
```

These reports are available only for the BC Stats / Statistics site (gov.bc.ca):
asset downloads, on-site search terms, and Google Search performance.

## Row {height=210px}

::: {.valuebox color="primary" title="Total Asset Downloads"}
`r comma(total_downloads)`
:::

::: {.valuebox color="info" title="Total Site Searches"}
`r comma(total_searches)`
:::

::: {.valuebox color="success" title="Total Google Clicks"}
`r comma(total_g_clicks)`
:::

::: {.valuebox color="secondary" title="Total Google Impressions"}
`r comma(total_g_impress)`
:::

## Row {height=500px}

### Daily Asset Downloads {width=45%}

```{r}
if (has_assets) {
  d <- asset_daily |> arrange(date)
  plot_ly(
    d, x = ~date, y = ~downloads, type = "scatter", mode = "lines",
    line = list(color = "#003366", width = 2),
    hovertemplate = "<b>%{x|%b %d, %Y}</b><br>Downloads: %{y:,}<extra></extra>"
  ) |>
    layout(
      title = list(text = "<b>Daily Asset Downloads</b>",
                   font = modifyList(bc_font, list(size = 15, color = "#003366"))),
      xaxis = list(title = "", gridcolor = "#e8ecf0", tickformat = "%b %d",
                   tickfont = modifyList(bc_font, list(size = 10, color = "#2d2d2d"))),
      yaxis = list(title = "", gridcolor = "#e8ecf0", automargin = TRUE,
                   tickfont = modifyList(bc_font, list(size = 10, color = "#5c6b7a"))),
      plot_bgcolor = "#ffffff", paper_bgcolor = "#ffffff",
      margin = list(l = 10, r = 20, t = 50, b = 30)
    ) |>
    config(
      displaylogo = plotly_config$displaylogo,
      modeBarButtonsToRemove = plotly_config$modeBarButtonsToRemove,
      responsive = plotly_config$responsive
    )
} else {
  plot_ly() |>
    add_annotations(text = "No asset download data available.", x = 0.5, y = 0.5,
                    xref = "paper", yref = "paper", showarrow = FALSE,
                    font = modifyList(bc_font, list(size = 13, color = "#5c6b7a"))) |>
    layout(xaxis = list(visible = FALSE), yaxis = list(visible = FALSE))
}
```

### Top Downloaded Assets {width=55%}

```{r}
if (has_assets && !is.null(top_assets)) {
  d <- top_assets |>
    mutate(
      fname = ifelse(is.na(asset_file) | asset_file == "", basename(asset_url), asset_file),
      full_label = coalesce(asset_url, fname),
      label = shorten_url(coalesce(asset_url, fname))
    ) |>
    arrange(desc(downloads)) |>
    slice_head(n = 15)

  plot_ly(
    d, x = ~downloads, y = ~label, orientation = "h",
    type = "bar",
    marker = list(color = "#1F6B75", line = list(color = "white", width = 0.5), opacity = 0.9),
    customdata = ~full_label,
    hovertemplate = "<b>%{customdata}</b><br>Downloads: %{x:,}<extra></extra>"
  ) |>
    layout(
      title = list(text = "<b>Top Downloaded Assets</b>",
                   font = modifyList(bc_font, list(size = 15, color = "#003366"))),
      xaxis = list(title = "", gridcolor = "#e8ecf0", zeroline = FALSE,
                   tickfont = modifyList(bc_font, list(size = 10, color = "#5c6b7a"))),
      yaxis = list(title = "", automargin = TRUE,
                   tickfont = modifyList(bc_font, list(size = 9, color = "#2d2d2d")),
                   categoryorder = "array", categoryarray = rev(d$label)),
      plot_bgcolor = "#ffffff", paper_bgcolor = "#ffffff",
      margin = list(l = 10, r = 30, t = 50, b = 30), bargap = 0.3
    ) |>
    config(
      displaylogo = plotly_config$displaylogo,
      modeBarButtonsToRemove = plotly_config$modeBarButtonsToRemove,
      responsive = plotly_config$responsive
    )
} else {
  plot_ly() |>
    add_annotations(text = "No asset data available.", x = 0.5, y = 0.5,
                    xref = "paper", yref = "paper", showarrow = FALSE,
                    font = modifyList(bc_font, list(size = 13, color = "#5c6b7a"))) |>
    layout(xaxis = list(visible = FALSE), yaxis = list(visible = FALSE))
}
```

## Row {height=520px}

### Top Site Search Terms {width=45%}

```{r}
if (has_search) {
  d <- search_terms |>
    arrange(desc(searches)) |>
    slice_head(n = 15)

  plot_ly(
    d, x = ~searches, y = ~search_term, orientation = "h",
    type = "bar",
    marker = list(color = "#6C3D8A", line = list(color = "white", width = 0.5), opacity = 0.9),
    hovertemplate = "<b>%{y}</b><br>Searches: %{x:,}<extra></extra>"
  ) |>
    layout(
      title = list(text = "<b>Top On-Site Search Terms</b>",
                   font = modifyList(bc_font, list(size = 15, color = "#003366"))),
      xaxis = list(title = "", gridcolor = "#e8ecf0", zeroline = FALSE,
                   tickfont = modifyList(bc_font, list(size = 10, color = "#5c6b7a"))),
      yaxis = list(title = "", automargin = TRUE,
                   tickfont = modifyList(bc_font, list(size = 10, color = "#2d2d2d")),
                   categoryorder = "array", categoryarray = rev(d$search_term)),
      plot_bgcolor = "#ffffff", paper_bgcolor = "#ffffff",
      margin = list(l = 10, r = 30, t = 50, b = 30), bargap = 0.3
    ) |>
    config(
      displaylogo = plotly_config$displaylogo,
      modeBarButtonsToRemove = plotly_config$modeBarButtonsToRemove,
      responsive = plotly_config$responsive
    )
} else {
  plot_ly() |>
    add_annotations(text = "No search data available.", x = 0.5, y = 0.5,
                    xref = "paper", yref = "paper", showarrow = FALSE,
                    font = modifyList(bc_font, list(size = 13, color = "#5c6b7a"))) |>
    layout(xaxis = list(visible = FALSE), yaxis = list(visible = FALSE))
}
```

### Top Google Search Queries {width=55%}

```{r}
if (has_google) {
  google_tbl <- google_queries |>
    arrange(desc(clicks)) |>
    slice_head(n = 50) |>
    transmute(
      Query = query,
      Page = page,
      Clicks = clicks,
      Impressions = impressions,
      CTR = percent(ctr, accuracy = 0.1)
    )

  datatable(
    google_tbl,
    options = list(pageLength = 12, scrollX = TRUE, order = list(list(2, "desc"))),
    rownames = FALSE
  )
} else {
  cat("No Google Search data available.")
}
```

# About

### About This Dashboard

**Maintainer / Contact**: Data Science Team

**Data Source**: CMS Lite report exports, downloaded from S3 by
`R/01d-get-cmslite-data.R` and summarized by `R/02c-analyze-cmslite-data.R`.

**Coverage**: Reporting period `r date_range_str`. The dashboard tracks three
CMS Lite sites:

- **Outcomes** — outcomes.bcstats.gov.bc.ca
- **Anti-Racism** — antiracism.gov.bc.ca
- **BC Stats / Statistics** — www2.gov.bc.ca/gov/content/data/statistics (and sub-themes)

**Reports per site**: daily page views by URL, daily clicks by target URL, daily
referring URLs, daily platforms (OS), and daily counts by province/country. The
BC Stats / Statistics site additionally provides asset download counts, on-site
search terms, and Google Search query performance.

**Engagement KPI**: "Page Views per Session" is total page views divided by total
sessions over the reporting period.

**How we build this**: Created with [Quarto Dashboards](https://quarto.org/docs/dashboards/)
in R, using `dplyr`, `ggplot2`, and `plotly`. The data extraction and rendering
code is open source.

**Source Code**: Find the source code on our [GitHub Repository](https://github.com/bcgov/bcstats-webtraffic-monitoring).
