---
title: "Shiny Dashboard Traffic Monitoring"
logo: "www/bcstats_logo_rev.png"
format: 
  dashboard:
    theme:
      - litera
      - theme.scss
    orientation: rows
    embed-resources: true
    nav-buttons:
      - icon: github
        href: https://github.com/bcgov/shinyapps-webtraffic-monitoring
---

<!-- 
HOW TO RUN THIS DASHBOARD FOR CODE REVIEW:
Option 1: In Positron or RStudio, open this file and click the "Render" button at the top.
Option 2: Run the following in the R Console: `quarto::quarto_render("Report/dashboard.qmd")`
Option 3: Run the following in the Terminal: `quarto preview Report/dashboard.qmd`
-->

```{r setup, include=FALSE}
library(readr)
library(dplyr)
library(knitr)
library(ggplot2)
library(forcats)
library(plotly)
library(lubridate)
library(safepaths)
library(glue)
library(DT)
library(scales)

# Define paths based on your 00-setup.R logic
# and the working directory during render is the R/ folder.
LAN_FOLDER <- use_network_path()
PROJECT_ROOT <- glue("{LAN_FOLDER}/0. Misc/Data Science Tooling/web-hosting-and-dashboards/shinyapps_webtraffic_monitoring")
OUTPUT_TABLES <- glue("{PROJECT_ROOT}/outputs/tables")
DATA_RAW <- glue("{PROJECT_ROOT}/data")

# Load summary data for value boxes
weekly_usage <- read_csv(file.path(OUTPUT_TABLES, "weekly_usage.csv"), show_col_types = FALSE)
visits_summary <- read_csv(file.path(OUTPUT_TABLES, "visits_minmax_summary.csv"), show_col_types = FALSE)
download_summary <- read_csv(file.path(OUTPUT_TABLES, "download_summary.csv"), show_col_types = FALSE)
daily_usage_raw <- readRDS(file.path(DATA_RAW, "daily_usage_raw.rds"))
download_data_raw <- readRDS(file.path(DATA_RAW, "download_data_raw.rds"))

app_abbr_map <- c(
  "Student Outcomes" = "SO",
  "popApp" = "POP",
  "LAEP" = "LAEP",
  "BCDS-DIP Linkage Rates" = "DIP",
  "BC Small Business" = "SB",
  "Economic-Indicators" = "ECON",
  "Household Projections" = "HHLD",
  "LFS app" = "LFS",
  "Interprovincial Migration" = "IM",
  "Country Trade Profiles" = "TRADE",
  "BC Retail Sales" = "RS"
)

# Safely map GA4's string isoYearIsoWeek to an actual Date object (Monday of that week)
week_date_map <- daily_usage_raw |>
  mutate(isoYearIsoWeek = format(as.Date(date), "%G%V")) |>
  summarize(week_date = min(as.Date(date), na.rm = TRUE), .by = isoYearIsoWeek)

weekly_usage <- weekly_usage |>
  mutate(
    app_abbr = coalesce(unname(app_abbr_map[pageTitle]), pageTitle),
    isoYearIsoWeek = as.character(isoYearIsoWeek) # FIX: Force to character before joining
  ) |>
  left_join(week_date_map, by = "isoYearIsoWeek") # Attach the real Date object for plotting

# For value boxes: calculate latest full week visits
latest_week <- max(weekly_usage$isoYearIsoWeek, na.rm = TRUE)
latest_week_data <- weekly_usage |> filter(isoYearIsoWeek == latest_week)
latest_week_date <- latest_week_data$week_date[1] # Extract Date for valuebox subtitle
latest_visits <- sum(latest_week_data$total_engaged_sessions, na.rm = TRUE) # change to total_sessions if you want raw visits instead of engaged sessions

# visits from the previous week for comparison (the week immediately before the latest full week)
previous_week <- max(weekly_usage$isoYearIsoWeek[weekly_usage$isoYearIsoWeek < latest_week], na.rm = TRUE)
previous_week_data <- weekly_usage |> filter(isoYearIsoWeek == previous_week)
prev_visits <- sum(previous_week_data$total_engaged_sessions, na.rm = TRUE) # change to total_sessions if you want raw visits instead of engaged sessions

# Calculate percent change and absolute change for value boxes
pct_change <- if (prev_visits > 0) {
  round((latest_visits - prev_visits) / prev_visits * 100, 1)
} else {
  NA
}
abs_change <- latest_visits - prev_visits

pct_change_str <- if (!is.na(pct_change)) {
  abs_sign <- if (abs_change > 0) "+" else ""
  paste0(abs_sign, abs_change, " visits; ", abs_sign, pct_change, "%")
} else {
  ""
}

# Total downloads for the latest full week (using ISO week formatting)
downloads_val <- download_data_raw |>
  mutate(iso_week = format(as.Date(date), "%G%V")) |>
  filter(iso_week == latest_week) |>
  summarize(total = sum(eventCount, na.rm = TRUE)) |>
  pull(total)
downloads_val <- if (length(downloads_val) == 0 || is.na(downloads_val)) 0L else downloads_val

# Shared Plotly branding helpers
bc_font <- list(family = "BC Sans, Segoe UI, Arial, sans-serif")

app_colors <- c(
  "SO"    = "#1F6B75", "POP"   = "#003366", "LAEP"  = "#6C3D8A",
  "DIP"   = "#C8373A", "SB"    = "#2F6B3F", "ECON"  = "#B07D12",
  "HHLD"  = "#7A5230", "LFS"   = "#1B5EA6", "IM"    = "#4A7C59",
  "TRADE" = "#9E4C1A", "RS"    = "#5B3A6E"
)

# Streamlined modebar: only reset + download image
plotly_config <- list(
  displaylogo = FALSE,
  modeBarButtonsToRemove = list(
    "zoom2d", "pan2d", "select2d", "lasso2d",
    "zoomIn2d", "zoomOut2d", "autoScale2d",
    "hoverClosestCartesian", "hoverCompareCartesian"
  ),
  responsive = TRUE
)
```

# Dashboard Summary {scrolling="true"}

## Row {height=210px}

::: {.valuebox color="primary" title="Total Visits Across All Dashboards (Week of `r format(latest_week_date, '%b %d, %Y')`)"}
`r comma(latest_visits)`
:::

::: {.valuebox color="`r if (abs_change >= 0) 'success' else 'warning'`" title="Change in Visits (Compared to week of `r format(latest_week_date - 7, '%b %d, %Y')`)"}
`r paste0(if (abs_change > 0) "+" else "", comma(abs_change))`
:::

::: {.valuebox color="`r if (pct_change >= 0) 'success' else 'warning'`" title="Percent Change from the week of `r format(latest_week_date - 7, '%b %d, %Y')`"}
`r if (!is.na(pct_change)) paste0(if (pct_change > 0) "+" else "", pct_change, "%") else "NA"`
:::

::: {.valuebox color="info" title="Total Downloads Across All Dashboards (Week of `r format(latest_week_date, '%b %d, %Y')`)"}
`r comma(downloads_val)`
:::

## Row {height=500px}

### Weekly Dashboard Visits Trend

```{r}
trend_apps  <- sort(unique(weekly_usage$app_abbr))
trend_palette <- c(
  "SO"    = "#1F6B75", "POP"   = "#003366", "LAEP"  = "#6C3D8A",
  "DIP"   = "#C8373A", "SB"    = "#2F6B3F", "ECON"  = "#B07D12",
  "HHLD"  = "#7A5230", "LFS"   = "#1B5EA6", "IM"    = "#4A7C59",
  "TRADE" = "#9E4C1A", "RS"    = "#5B3A6E"
)

trend_data <- weekly_usage |>
  filter(week_date >= as.Date("2025-07-01"))

# Build one trace per app
trend_traces <- lapply(trend_apps, function(app_i) {
  d <- trend_data |> filter(app_abbr == app_i) |> arrange(week_date)
  list(
    x             = d$week_date,
    y             = d$total_engaged_sessions,
    type          = "scatter",
    mode          = "lines",
    name          = app_i,
    line          = list(color = unname(trend_palette[app_i]), width = 2),
    hovertemplate = paste0("<b>", app_i, "</b><br>Week of: %{x|%b %d, %Y}<br>Sessions: %{y:,}<extra></extra>")
  )
})

p_trend <- plot_ly()
for (tr in trend_traces) {
  p_trend <- add_trace(p_trend,
    x = tr$x, y = tr$y,
    type = tr$type, mode = tr$mode,
    name = tr$name, line = tr$line,
    hovertemplate = tr$hovertemplate
  )
}

p_trend |>
  layout(
    title = list(
      text = "<b>Weekly Dashboard Visits Trend (from July 2025)</b>",
      font = modifyList(bc_font, list(size = 15, color = "#003366"))
    ),
    xaxis = list(
      title    = "",
      tickfont = modifyList(bc_font, list(size = 11, color = "#2d2d2d")),
      gridcolor = "#e8ecf0",
      tickformat = "%b %Y"
    ),
    yaxis = list(
      title    = "",
      tickfont = modifyList(bc_font, list(size = 11, color = "#5c6b7a")),
      gridcolor = "#e8ecf0",
      automargin = TRUE
    ),
    legend = list(
      orientation = "h",
      x = 0, y = -0.15,
      font = modifyList(bc_font, list(size = 10)),
      title = list(text = "")
    ),
    annotations = list(list(
      text      = "Tip: Click a dashboard in the legend to isolate its trend; click again to reset.",
      x = 1, y = -0.22, xref = "paper", yref = "paper",
      xanchor = "right", yanchor = "top",
      showarrow = FALSE,
      font = modifyList(bc_font, list(size = 10, color = "#8a9bac"))
    )),
    plot_bgcolor  = "#ffffff",
    paper_bgcolor = "#ffffff",
    margin = list(l = 10, r = 20, t = 50, b = 80)
  ) |>
  layout(legend = list(itemclick = "toggleothers", itemdoubleclick = "toggle")) |>
  config(
    displaylogo            = plotly_config$displaylogo,
    modeBarButtonsToRemove = plotly_config$modeBarButtonsToRemove,
    responsive             = plotly_config$responsive
  )
```

## Row {height=620px}

### Total Time on Dashboard by Dashboard

```{r}
time_data <- daily_usage_raw |>
  filter(pageTitle %in% names(app_abbr_map)) |>
  mutate(
    date = as.Date(date),
    iso_week = format(date, "%G%V"), 
    weekday = wday(date, label = TRUE, abbr = TRUE, week_start = 1),
    total_time_mins = userEngagementDuration / 60
  )

# Aggregate to weekday totals by app for latest and previous week
time_compare <- time_data |>
  filter(iso_week %in% c(latest_week, previous_week)) |>
  mutate(
    period = if_else(iso_week == latest_week, "Latest Week", "Previous Week"),
    app = coalesce(unname(app_abbr_map[pageTitle]), pageTitle)
  ) |>
  summarize(total_time = sum(total_time_mins, na.rm = TRUE), .by = c(app, weekday, period)) |>
  mutate(
    weekday = factor(
      as.character(weekday),
      levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun")
    )
  )

apps <- sort(unique(time_compare$app))
weekdays_ordered <- c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun")

default_app <- if ("POP" %in% apps) "POP" else apps[1]

period_colors <- list(
  "Latest Week"   = "#003366",
  "Previous Week" = "#8fa8c8"
)

traces <- list()
for (i in seq_along(apps)) {
  app_i   <- apps[i]
  d       <- time_compare |> filter(app == app_i)
  visible <- app_i == default_app

  for (period_i in c("Latest Week", "Previous Week")) {
    d_p <- d |> filter(period == period_i) |> arrange(weekday)
    traces <- c(traces, list(list(
      x    = as.character(d_p$weekday),
      y    = d_p$total_time,
      type = "scatter",
      mode = "lines+markers",
      name = period_i,
      line = list(
        dash  = if (period_i == "Latest Week") "solid" else "dash",
        color = period_colors[[period_i]],
        width = 2.5
      ),
      marker = list(
        size  = 7,
        color = period_colors[[period_i]],
        line  = list(color = "white", width = 1)
      ),
      visible       = visible,
      hovertemplate = paste0(
        "<b>", app_i, " \u2013 ", period_i, "</b><br>",
        "%{x}: %{y:.1f} min<extra></extra>"
      ),
      showlegend = visible
    )))
  }
}

n_traces <- length(traces)

# y-axis title is folded into the plot title via button updates — no separate axis label
buttons <- lapply(seq_along(apps), function(i) {
  app_i        <- apps[i]
  visible      <- rep(FALSE, n_traces)
  idx          <- c((i - 1) * 2 + 1, (i - 1) * 2 + 2)
  visible[idx] <- TRUE

  app_vals <- time_compare |> filter(app == app_i) |> pull(total_time)
  y_max    <- max(app_vals, na.rm = TRUE) * 1.15

  list(
    method = "update",
    args   = list(
      list(visible = as.list(visible), showlegend = as.list(visible)),
      list(
        title = list(
          text    = paste0("<b>Total Time on Dashboard (Minutes) by Day of Week \u2013 ", app_i, "</b>"),
          font    = modifyList(bc_font, list(size = 15, color = "#003366"))
        ),
        yaxis = list(
          title      = "",          # label removed; unit in plot title
          range      = list(0, y_max),
          automargin = TRUE,
          tickfont   = modifyList(bc_font, list(size = 10, color = "#5c6b7a")),
          gridcolor  = "#e8ecf0"
        )
      )
    ),
    label = app_i
  )
})

first_vals <- time_compare |> filter(app == default_app) |> pull(total_time)
y_max_init <- max(first_vals, na.rm = TRUE) * 1.15

plot_ly() |>
  (\(p) Reduce(function(acc, tr) add_trace(acc,
    x             = tr$x,    y          = tr$y,
    type          = tr$type, mode       = tr$mode,
    name          = tr$name,
    line          = tr$line, marker     = tr$marker,
    visible       = tr$visible,
    hovertemplate = tr$hovertemplate,
    showlegend    = tr$showlegend
  ), traces, init = p))() |>
  layout(
    title = list(
      text    = paste0("<b>Total Time (Minutes) on Dashboard by Day of Week \u2013 ", default_app, "</b>"),
      font    = modifyList(bc_font, list(size = 15, color = "#003366"))
    ),
    xaxis = list(
      title         = "",
      categoryorder = "array",
      categoryarray = weekdays_ordered,
      tickfont      = modifyList(bc_font, list(size = 11, color = "#2d2d2d", bold = TRUE)),
      gridcolor     = "#e8ecf0"
    ),
    yaxis = list(
      title      = "",
      range      = list(0, y_max_init),
      automargin = TRUE,
      tickfont   = modifyList(bc_font, list(size = 10, color = "#5c6b7a")),
      gridcolor  = "#e8ecf0"
    ),
    legend = list(
      orientation = "h", x = 0, y = 1.08,
      font        = modifyList(bc_font, list(size = 11))
    ),
    annotations = list(
      list(
        text      = "Tip: Use the dropdown to switch dashboards.",
        x = 1, y = -0.1, xref = "paper", yref = "paper",
        xanchor   = "right", yanchor = "top",
        showarrow = FALSE,
        font      = modifyList(bc_font, list(size = 10, color = "#8a9bac"))
      )
    ),
    updatemenus = list(list(
      type        = "dropdown",
      direction   = "down",
      x           = 0.0, xanchor = "left",
      y           = 1.22, yanchor = "top",
      buttons     = buttons,
      active      = which(apps == default_app) - 1L,
      showactive  = TRUE,
      bgcolor     = "#f5f8fb",
      bordercolor = "#c8d8e8",
      font        = modifyList(bc_font, list(size = 11))
    )),
    plot_bgcolor  = "#ffffff",
    paper_bgcolor = "#ffffff",
    margin = list(l = 60, r = 20, t = 75, b = 60)
  ) |>
  config(
    displaylogo            = plotly_config$displaylogo,
    modeBarButtonsToRemove = plotly_config$modeBarButtonsToRemove,
    responsive             = plotly_config$responsive
  )
```

## Row {height=520px}

### Dashboard Downloads by App and File

```{r}
download_plot_data <- download_data_raw |>
  mutate(
    iso_week = format(as.Date(date), "%G%V")
  ) |>
  filter(iso_week == latest_week) |>
  summarize(total_downloads = sum(eventCount, na.rm = TRUE), .by = c(pageTitle, file_label)) |>
  mutate(
    app = coalesce(unname(app_abbr_map[pageTitle]), pageTitle),
    file_clean = case_when(
      is.na(file_label) | file_label == "" | file_label == "(not set)" ~ "Unknown File",
      grepl("^/", file_label) ~ basename(file_label),
      TRUE ~ file_label
    ),
    label = paste0(app, ": ", file_clean)
  ) |>
  arrange(desc(total_downloads)) |>
  slice_head(n = 25)

if (nrow(download_plot_data) > 0) {
  avg_downloads <- mean(download_plot_data$total_downloads, na.rm = TRUE)
  label_order  <- download_plot_data |> arrange(total_downloads) |> pull(label)

  bar_colors <- unname(app_colors[download_plot_data$app])
  bar_colors[is.na(bar_colors)] <- "#888888"

  plot_ly() |>
    add_bars(
      data = download_plot_data,
      x = ~total_downloads,
      y = ~factor(label, levels = label_order),
      orientation = "h",
      marker = list(
        color  = bar_colors,
        line   = list(color = "white", width = 0.5),
        opacity = 0.88
      ),
      customdata = ~pageTitle,
      hovertemplate = paste0(
        "<b>%{y}</b><br>",
        "Dashboard: %{customdata}<br>",
        "Downloads: %{x:,}<extra></extra>"
      ),
      showlegend = FALSE
    ) |>
    layout(
      title = list(
        text  = "<b>Total Downloads by Dashboard & File — Latest Week</b>",
        font  = modifyList(bc_font, list(size = 15, color = "#003366"))
      ),
      xaxis = list(
        title     = "",
        tickfont  = modifyList(bc_font, list(size = 10, color = "#5c6b7a")),
        gridcolor = "#e8ecf0",
        zeroline  = FALSE
      ),
      yaxis = list(
        title      = "",
        automargin = TRUE,
        tickfont   = modifyList(bc_font, list(size = 10, color = "#2d2d2d"))
      ),
      shapes = list(list(
        type = "line",
        x0 = avg_downloads, x1 = avg_downloads,
        y0 = 0, y1 = 1,
        xref = "x", yref = "paper",
        line = list(color = "#fcba19", width = 1.5, dash = "dash")
      )),
      annotations = list(
        list(
          x = avg_downloads, y = 1,
          xref = "x", yref = "paper",
          text = paste0("Avg: ", round(avg_downloads, 1)),
          showarrow  = FALSE,
          xanchor    = "left",
          bgcolor    = "rgba(255,255,255,0.85)",
          borderpad  = 3,
          font       = modifyList(bc_font, list(size = 10, color = "#333333"))
        )
      ),
      plot_bgcolor  = "#ffffff",
      paper_bgcolor = "#ffffff",
      margin = list(l = 10, r = 30, t = 45, b = 30),
      bargap = 0.3
    ) |>
    config(
      displaylogo          = FALSE,
      modeBarButtonsToRemove = list(
        "zoom2d", "pan2d", "select2d", "lasso2d",
        "zoomIn2d", "zoomOut2d", "autoScale2d",
        "hoverClosestCartesian", "hoverCompareCartesian"
      ),
      responsive = TRUE
    )
} else {
  plot_ly() |>
    add_annotations(
      text = "No download data available for the latest week.",
      x = 0.5, y = 0.5, xref = "paper", yref = "paper",
      showarrow = FALSE,
      font = modifyList(bc_font, list(size = 13, color = "#5c6b7a"))
    ) |>
    layout(xaxis = list(visible = FALSE), yaxis = list(visible = FALSE))
}
```

# Dashboard Details {scrolling="true"}

```{r details-data, include=FALSE}
usage_summary_det  <- read_csv(file.path(OUTPUT_TABLES, "usage_summary.csv"),   show_col_types = FALSE)
location_summary   <- read_csv(file.path(OUTPUT_TABLES, "location_summary.csv"), show_col_types = FALSE)
device_summary     <- read_csv(file.path(OUTPUT_TABLES, "device_summary.csv"),  show_col_types = FALSE)
browser_summary    <- read_csv(file.path(OUTPUT_TABLES, "browser_summary.csv"), show_col_types = FALSE)
```

## Row

### Per-Dashboard Details

Expand any dashboard below to see its recent usage stats, top visitor locations, device types, and browsers.

```{r details-accordions, results="asis"}
detail_apps <- sort(unique(usage_summary_det$pageTitle))

for (app_i in detail_apps) {
  abbr_i <- coalesce(unname(app_abbr_map[app_i]), app_i)

  cat(glue('\n\n::: {{.callout-note collapse="true"}}\n## {abbr_i} \u2014 {app_i}\n\n'))

  # --- Usage snapshot ---
  u <- usage_summary_det |> filter(pageTitle == app_i)
  engaged_min <- round(u$avg_engaged_seconds_per_user / 60, 1)
  cat(glue(
    "**Recent week sessions:** {scales::comma(u$recent_week_sessions)} &nbsp;|&nbsp; ",
    "**4-wk rolling avg sessions:** {scales::comma(round(u$rolling_sessions_week, 0))} &nbsp;|&nbsp; ",
    "**Avg engaged time/user:** {engaged_min} min\n\n"
  ))

  # --- Top locations ---
  loc <- location_summary |>
    filter(pageTitle == app_i) |>
    arrange(desc(total_active_users)) |>
    slice_head(n = 10) |>
    select(Country = country, Region = region, City = city, Users = total_active_users)

  if (nrow(loc) > 0) {
    cat("**Top Visitor Locations**\n\n")
    cat(knitr::kable(loc, format = "html",
      table.attr = 'class="table table-sm table-striped" style="font-size:0.85em;"'))
    cat("\n\n")
  }

  # --- Device breakdown ---
  dev <- device_summary |>
    filter(pageTitle == app_i) |>
    arrange(desc(total_active_users)) |>
    mutate(Share = scales::percent(pct_users, accuracy = 1)) |>
    select(Device = deviceCategory, Users = total_active_users, Share)

  if (nrow(dev) > 0) {
    cat("**Device Breakdown**\n\n")
    cat(knitr::kable(dev, format = "html",
      table.attr = 'class="table table-sm" style="font-size:0.85em; width:auto;"'))
    cat("\n\n")
  }

  # --- Browser breakdown (top 5) ---
  brow <- browser_summary |>
    filter(pageTitle == app_i) |>
    arrange(desc(total_active_users)) |>
    slice_head(n = 5) |>
    mutate(Share = scales::percent(pct_users, accuracy = 1)) |>
    select(Browser = browser, Users = total_active_users, Share)

  if (nrow(brow) > 0) {
    cat("**Top Browsers**\n\n")
    cat(knitr::kable(brow, format = "html",
      table.attr = 'class="table table-sm" style="font-size:0.85em; width:auto;"'))
    cat("\n\n")
  }

  cat(":::\n")
}
```

## Row

### Overall Summary Statistics

::: {.callout-tip collapse="true"}
## Column Descriptions

| Column | Description |
|--------|-------------|
| **Weekly Visits — Min / Avg / Max** | Number of sessions in a single week. Min = quietest week, Max = busiest, Avg = typical. |
| **Time on Page — Min / Avg / Max (min)** | Total user engagement time per week in **minutes** (active foreground time from GA4). |
| **Avg Weekly Downloads** | Average file download events per week (CSV, Excel, PDF exports). |
:::

```{r}
visits_summary_clean <- visits_summary |>
  mutate(
    app_abbr = coalesce(unname(app_abbr_map[pageTitle]), pageTitle),
    pageTitle = paste0(pageTitle, " (", app_abbr, ")")
  ) |>
  select(-app_abbr, -median_weekly_visits) |>
  rename(
    `Dashboard` = pageTitle,
    `Visits Min` = min_weekly_visits,
    `Visits Avg` = avg_weekly_visits,
    `Visits Max` = max_weekly_visits,
    `Time Min (min)` = min_time_min,
    `Time Avg (min)` = avg_time_min,
    `Time Max (min)` = max_time_min,
    `Avg Weekly Downloads` = avg_weekly_downloads
  ) |>
  mutate(across(where(is.numeric), round, 1))

datatable(
  visits_summary_clean,
  options = list(pageLength = 11, dom = 't', scrollX = TRUE)
)
```

# About

### About This Dashboard

**Maintainer / Contact**: Data Science Team

**Data Source**: Data is pulled automatically via the Google Analytics 4 (GA4) API using a scheduled R script.

**How we build this**: This dashboard was created using [Quarto Dashboards](https://quarto.org/docs/dashboards/) in R, leveraging libraries like `ggplot2`, `plotly`, and `googleAnalyticsR`. The source code for extracting data and rendering the tool is open source!

**Source Code**: Find the source code on our [GitHub Repository](https://github.com/bcgov/shinyapps-webtraffic-monitoring).